Chromosomal duplication can be an evolutionary detour on the path to adaptation

### 2022-09-11 ms/ms.tex
added mutation tables

\usepackage{amssymb,amsmath,amsthm}
\usepackage{commath}
\usepackage{longtable}
\usepackage[hyphens]{url}
\usepackage[dvipsnames]{xcolor}
\usepackage[unicode=true,colorlinks=true,urlcolor=CadetBlue,citecolor=black,linkcolor=black]{hyperref}
\usepackage{booktabs}
\usepackage{pgfplotstable} 
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage{authblk}
\usepackage{subcaption}
\captionsetup[subfigure]{labelformat=empty}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{longtable}
\usepackage{gensymb,siunitx}
\usepackage{cleveref}

@@

\paragraph{Empirical frequencies of mutant alleles.} 
For each of two evolved populations ($H2$ and $H4$) we sequenced the ancestral population (generation 0), the aneuploid population (generation 450), and the evolved euploid population (generation 1,700 or 2,350) to estimate the mutant allele frequencies (\Cref{table:mutations}). % TODO add table!!
Overall, between 100 and 173 mutant alleles were detected with at least a single read in the six populations that were sampled. 
Disregarding 45 and 40 alleles that were present in the ancestral populations at a frequency >10\%, the aneuploid and euploid populations carried a large number of mutant alleles: 82 and 95, respectively, in repetition $H2$, and 60 and 66 in repetition $H4$.

@@

@@

%TODO table:mutations

>>>>

\usepackage{amssymb,amsmath,amsthm}
\usepackage{commath}
\usepackage{longtable}
\usepackage[hyphens]{url}
\usepackage[dvipsnames]{xcolor}
\usepackage[unicode=true,colorlinks=true,urlcolor=CadetBlue,citecolor=black,linkcolor=black]{hyperref}
\usepackage{booktabs}
\usepackage{pgfplotstable} % http://mirrors.ctan.org/graphics/pgf/contrib/pgfplots/doc/pgfplotstable.pdf
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage{authblk}
\usepackage{subcaption}
\captionsetup[subfigure]{labelformat=empty}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{longtable}
\usepackage{gensymb,siunitx}
\usepackage{cleveref}

@@

\paragraph{Empirical frequencies of mutant alleles.} 
For each of two evolved populations ($H2$ and $H4$) we sequenced the ancestral population (generation 0), the aneuploid population (generation 450), and the evolved euploid population (generation 1,700 or 2,350) to estimate the mutant allele frequencies (\Cref{table:mutations_H2,table:mutations_H4}). 
Overall, between 100 and 173 mutant alleles were detected with at least a single read in the six populations that were sampled. 
Disregarding 45 and 40 alleles that were present in the ancestral populations at a frequency >10\%, the aneuploid and euploid populations carried a large number of mutant alleles: 82 and 95, respectively, in repetition $H2$, and 60 and 66 in repetition $H4$.

@@

% Table - mutations
%% generated with mutation_analysis.ipynb
\begin{table}[h]
\centering
\caption{
\textbf{Mutant alleles in population $H2$.}}
\caption*{
	Mutant alleles identified in the ancestor (generation 0), aneuploid (generation 450), and evolved (generation 1,700) of population $H2$. See supplementary file.
} 
\label{table:mutations_H2}
\end{table}

% Table - mutations
%% generated with mutation_analysis.ipynb
\begin{table}[h]
\centering
\caption{
\textbf{Mutant alleles in population $H4$.}}
\caption*{
	Mutant alleles identified in the ancestor (generation 0), aneuploid (generation 450), and evolved (generation 2,350) of population $H4$. See supplementary file.
} 
\label{table:mutations_H4}
\end{table}

@@
